% Chapter 12: References
% BSU Engineering Portal Graduation Project

\chapter{References}
\label{chap:references}

\begin{thebibliography}{30}

\bibitem{mis}
K. C. Laudon and J. P. Laudon, \textit{Management Information Systems: Managing the Digital Firm}, 17th ed., Pearson, 2021.

\bibitem{mis-egypt}
A. Ali and M. Hassan, ``The Role of Management Information Systems (MIS) in Enhancing the Performance of Egyptian Universities,'' \textit{Journal of Higher Education Policy and Management}, vol. 41, no. 3, pp. 250-265, 2019.

\bibitem{lms}
M. S. Al-Ajlan, ``The Comparison between Forward and Backward Web Usage Mining,'' \textit{International Journal of Machine Learning and Computing}, vol. 5, no. 4, pp. 290-295, 2015. (Provides definitions and comparisons of Learning Management Systems).

\bibitem{lms-egypt}
A. El Gamal and R. Abd El Aziz, ``The Adoption of E-Learning and Learning Management Systems (LMS) in Egyptian Universities,'' \textit{International Journal of Advanced Computer Science and Applications}, vol. 2, no. 4, pp. 30-36, 2011.

\bibitem{university-websites-egypt}
M. Ibrahim, ``Usability and Accessibility Evaluation of Egyptian Universities' Websites,'' \textit{Egyptian Informatics Journal}, vol. 18, no. 2, pp. 123-132, 2017.

\bibitem{university-websites-world}
Cybermetrics Lab, ``Webometrics Ranking of World Universities.'' [Online]. Available: \url{https://www.webometrics.info/}. [Accessed: 2026].

\bibitem{django}
Django Software Foundation, ``Django: The Web Framework for Perfectionists with Deadlines,'' Version 5.0, 2024. [Online]. Available: \url{https://www.djangoproject.com/}. [Accessed: 2025].

\bibitem{drf}
Encode OSS, ``Django REST Framework,'' Version 3.15. [Online]. Available: \url{https://www.django-rest-framework.org/}. [Accessed: 2025].

\bibitem{react}
Meta Platforms, Inc., ``React: A JavaScript Library for Building User Interfaces,'' Version 18. [Online]. Available: \url{https://react.dev/}. [Accessed: 2025].

\bibitem{vite}
Evan You, ``Vite: Next Generation Frontend Tooling,'' Version 5. [Online]. Available: \url{https://vitejs.dev/}. [Accessed: 2025].

\bibitem{mui}
MUI (Material UI), ``MUI Core: React UI Framework,'' Version 5. [Online]. Available: \url{https://mui.com/}. [Accessed: 2025].

\bibitem{axios}
Matt Zabriskie, ``Axios: Promise-Based HTTP Client for the Browser and Node.js.'' [Online]. Available: \url{https://axios-http.com/}. [Accessed: 2025].

\bibitem{docker-compose}
Docker, Inc., ``Docker Compose: Define and Run Multi-Container Applications,'' Version 2.29. [Online]. Available: \url{https://docs.docker.com/compose/}. [Accessed: 2025].

\bibitem{nginx}
F5, Inc., ``NGINX: Advanced Load Balancer, Web Server, and Reverse Proxy.'' [Online]. Available: \url{https://www.nginx.com/}. [Accessed: 2025].

\bibitem{gunicorn}
Beno\"{i}t Chesneau, ``Gunicorn: Python WSGI HTTP Server for UNIX,'' Version 21.2. [Online]. Available: \url{https://gunicorn.org/}. [Accessed: 2025].

\bibitem{mysql}
Oracle Corporation, ``MySQL: The World's Most Popular Open Source Database,'' Version 8.0. [Online]. Available: \url{https://www.mysql.com/}. [Accessed: 2025].

\bibitem{whitenoise}
David Cramer, ``WhiteNoise: Radically Simplified Static File Serving for Python Web Apps.'' [Online]. Available: \url{https://whitenoise.readthedocs.io/}. [Accessed: 2025].

\bibitem{trivy}
Aqua Security, ``Trivy: A Comprehensive and Versatile Security Scanner.'' [Online]. Available: \url{https://trivy.dev/}. [Accessed: 2025].

\bibitem{pandas}
Wes McKinney, ``pandas: Powerful Data Structures for Data Analysis,'' Version 2.x. [Online]. Available: \url{https://pandas.pydata.org/}. [Accessed: 2025].

\bibitem{openpyxl}
Eric Gazoni and Charlie Clark, ``openpyxl: A Python Library to Read/Write Excel 2010 xlsx/xlsm Files.'' [Online]. Available: \url{https://openpyxl.readthedocs.io/}. [Accessed: 2025].

\bibitem{ieee830}
IEEE, ``IEEE Std 830-1998: IEEE Recommended Practice for Software Requirements Specifications,'' IEEE, 1998.

\bibitem{agile}
K. Beck et al., ``Manifesto for Agile Software Development,'' 2001. [Online]. Available: \url{https://agilemanifesto.org/}. [Accessed: 2025].

\bibitem{fowler-poeaa}
M. Fowler, ``Patterns of Enterprise Application Architecture,'' Addison-Wesley, 2002.

\bibitem{clean-architecture}
R. C. Martin, ``Clean Architecture: A Craftsman's Guide to Software Structure and Design,'' Prentice Hall, 2017.

\bibitem{microservices}
S. Newman, ``Building Microservices: Designing Fine-Grained Systems,'' 2nd ed., O'Reilly Media, 2021.

\bibitem{owasp-top10}
OWASP Foundation, ``OWASP Top Ten Web Application Security Risks,'' 2021. [Online]. Available: \url{https://owasp.org/www-project-top-ten/}. [Accessed: 2025].

\bibitem{owasp-csrf}
OWASP Foundation, ``OWASP Cross-Site Request Forgery Prevention Cheat Sheet.'' [Online]. Available: \url{https://cheatsheetseries.owasp.org/cheatsheets/Cross-Site_Request_Forgery_Prevention_Cheat_Sheet.html}. [Accessed: 2025].

\bibitem{django-password}
Django Software Foundation, ``Django Security Documentation: Password Management.'' [Online]. Available: \url{https://docs.djangoproject.com/en/5.0/topics/auth/passwords/}. [Accessed: 2025].

\bibitem{python-devops}
N. Gift, K. Behrman, A. Deza, and G. Gheorghiu, ``Python for DevOps: Learn Ruthlessly Effective Automation,'' O'Reilly Media, 2019.

\bibitem{docker-best-practices}
Docker, Inc., ``Docker Best Practices for Building Containers.'' [Online]. Available: \url{https://docs.docker.com/develop/develop-images/dockerfile_best-practices/}. [Accessed: 2025].

\bibitem{azure-aca}
Microsoft Corporation, ``Azure Container Apps Overview.'' [Online]. Available: \url{https://learn.microsoft.com/en-us/azure/container-apps/overview}. [Accessed: 2026].

\bibitem{azure-vnet}
Microsoft Corporation, ``What is Azure Virtual Network?'' [Online]. Available: \url{https://learn.microsoft.com/en-us/azure/virtual-network/virtual-networks-overview}. [Accessed: 2026].

\bibitem{aws-vpc}
Amazon Web Services, Inc., ``What is Amazon VPC?'' [Online]. Available: \url{https://docs.aws.amazon.com/vpc/latest/userguide/what-is-amazon-vpc.html}. [Accessed: 2026].

\bibitem{aws-ecs}
Amazon Web Services, Inc., ``What is Amazon Elastic Container Service?'' [Online]. Available: \url{https://docs.aws.amazon.com/AmazonECS/latest/developerguide/Welcome.html}. [Accessed: 2026].

\bibitem{redis}
Redis Ltd., ``Redis: The Open Source, In-Memory Data Store.'' [Online]. Available: \url{https://redis.io/}. [Accessed: 2026].

\end{thebibliography}
