% Chapter 10: Limitations & Future Work
% BSU Engineering Portal Graduation Project

\chapter{Limitations and Future Work}
\label{chap:limitations}

A mature engineering project acknowledges its boundaries. This chapter documents the system's known limitations with full transparency---not as failures, but as \textbf{deliberate scope decisions} and \textbf{honest assessments} of what the current architecture does not yet support. Each limitation is paired with a concrete proposed mitigation, providing a roadmap for future development.

\section{Known Limitations}
\label{sec:limitations}

\subsection{Architectural Limitations}

\begingroup
\small
\renewcommand{\arraystretch}{1.3}
\begin{longtable}{|c|p{2.5cm}|c|p{3.5cm}|p{4.5cm}|}
    \hline
    \textbf{ID} & \textbf{Limitation} & \textbf{Category} & \textbf{Impact} & \textbf{Proposed Mitigation} \\
    \hline
    \endfirsthead
    \hline
    \textbf{ID} & \textbf{Limitation} & \textbf{Category} & \textbf{Impact} & \textbf{Proposed Mitigation} \\
    \hline
    \endhead
    \hline
    \endfoot
    L-01 & \textbf{No horizontal scaling} & Architecture & Single-server deployment. Under extreme load ($>$5,000 concurrent users), Gunicorn's~\cite{gunicorn} 2 workers become a bottleneck. & Add Docker Swarm or Kubernetes with multiple backend replicas behind a load balancer. Redis session store already enables this. \\
    \hline
    L-02 & \textbf{Monolithic Django~\cite{django} application} & Architecture & All four Django apps share a single database and process. A bug in the quiz engine could affect attendance recording. & For current scale (\textasciitilde2,000 students), monolithic is correct. Microservices justified only above \textasciitilde10,000 users or with independent deployment requirements. \\
    \hline
    L-03 & \textbf{No WebSocket / real-time updates} & Architecture & Dashboards require manual refresh to see new data. A student must refresh to see a newly published grade. & Integrate Django Channels with Redis channel layer for WebSocket-based push notifications. Estimated effort: 2-3 sprints. \\
    \hline
    L-04 & \textbf{Synchronous Gunicorn workers} & Architecture & Long-running operations (large Excel uploads) block a worker. With 2 workers, this can cause queuing. & Migrate to async workers (\texttt{uvicorn} + ASGI) or offload tasks to Celery with Redis as message broker. \\
    \hline
    L-05 & \textbf{No database read replicas} & Infrastructure & All read and write queries hit the same MySQL~\cite{mysql} instance. Heavy reporting queries compete with real-time CRUD. & Add MySQL read replica for reporting queries. Django's \texttt{DATABASE\_ROUTERS} supports routing reads to separate database. \\
    \hline
    \caption{Architectural Limitations and Proposed Mitigations}
    \label{tab:arch-limitations}
\end{longtable}
\endgroup

\newpage
\subsection{Feature Limitations}

\begingroup
\small
\renewcommand{\arraystretch}{1.3}
\begin{longtable}{|c|p{2.5cm}|c|p{3.5cm}|p{4.5cm}|}
    \hline
    \textbf{ID} & \textbf{Limitation} & \textbf{Category} & \textbf{Impact} & \textbf{Proposed Mitigation} \\
    \hline
    \endfirsthead
    \hline
    \textbf{ID} & \textbf{Limitation} & \textbf{Category} & \textbf{Impact} & \textbf{Proposed Mitigation} \\
    \hline
    \endhead
    \hline
    \endfoot
    L-07 & \textbf{No mobile native application} & Feature & Responsive web serves mobile users but lacks offline capability, push notifications, and native camera access. & Develop React Native companion app or implement PWA with service workers for offline-first. \\
    \hline
    L-08 & \textbf{No real-time chat / messaging} & Feature & Communication is one-directional (admin $\rightarrow$ users via announcements). No student-doctor messaging. & Implement Django Channels for WebSocket-based messaging. Requires Redis/RabbitMQ broker and chat UI. \\
    \hline
    L-09 & \textbf{No email/SMS notifications} & Feature & Users must log in to discover new announcements, grades, or quiz availability. & Integrate Django's email backend with SMTP provider (SendGrid, Mailgun). SMS requires Twilio/Vonage. \\
    \hline
    L-10 & \textbf{No advanced analytics / reporting} & Feature & System records data but does not generate statistical reports (GPA distributions, attendance trends). & Build reporting dashboard using Chart.js or Recharts, with Django aggregation queries providing data. \\
    \hline
    L-11 & \textbf{No automated exam proctoring} & Feature & Online quizzes have no anti-cheating mechanisms beyond time limits. & Integrate browser lockdown APIs, webcam monitoring, or third-party proctoring services. Requires AI/ML. \\
    \hline
    L-12 & \textbf{No multi-language support} & Feature & Interface is Arabic-only. No option for English-speaking faculty. & Implement Django's~\cite{django} i18n framework with \texttt{gettext} translations. React~\cite{react} frontend uses \texttt{react-i18next}. \\
    \hline
    L-13 & \textbf{Single quiz attempt only} & Feature & Students can only take each quiz once. No mechanism for retakes or practice modes. & Add \texttt{max\_attempts} field to Quiz model. Modify \texttt{unique\_together} to \texttt{['student', 'quiz', 'attempt\_number']}. \\
    \hline
    L-14 & \textbf{No GPA calculation} & Feature & System records individual course grades but does not compute cumulative or semester GPA. & Add GPA calculation service that aggregates \texttt{StudentGrade.total\_grade()} across courses, weighted by credit hours. \\
    \hline
    L-19 & \textbf{No discussion forums} & Feature & Students and doctors lack a structured platform for asynchronous academic discussions. & Implement a forum module with topic threads, replies, and moderation tools. \\
    \hline
    L-20 & \textbf{No live virtual classrooms} & Feature & System does not support real-time remote lectures or video conferencing. & Integrate with Zoom/Teams APIs or embed an open-source solution like BigBlueButton. \\
    \hline
    \caption{Feature Limitations and Proposed Mitigations}
    \label{tab:feature-limitations}
\end{longtable}
\endgroup

\newpage
\subsection{Operational Limitations}

\begingroup
\small
\renewcommand{\arraystretch}{1.3}
\begin{longtable}{|c|p{2.5cm}|c|p{3.5cm}|p{4.5cm}|}
    \hline
    \textbf{ID} & \textbf{Limitation} & \textbf{Category} & \textbf{Impact} & \textbf{Proposed Mitigation} \\
    \hline
    \endfirsthead
    \hline
    \textbf{ID} & \textbf{Limitation} & \textbf{Category} & \textbf{Impact} & \textbf{Proposed Mitigation} \\
    \hline
    \endhead
    \hline
    \endfoot
    L-15 & \textbf{No automated backup strategy} & Operations & Database persistence relies on Docker~\cite{docker} volumes. If host disk fails, all data is lost. & Implement scheduled MySQL dumps (\texttt{mysqldump}) to cloud storage (S3, GCS) via cron job. Daily backups with 30-day retention. \\
    \hline
    L-16 & \textbf{No monitoring / alerting} & Operations & No system health dashboard or automated alerting for container failures, high CPU, or DB exhaustion. & Deploy Prometheus + Grafana for metrics. Add Alertmanager for email/Slack notifications on critical events. \\
    \hline
    L-17 & \textbf{No HTTPS in default config} & Operations & Default Nginx configuration serves HTTP on port 80. HTTPS requires manual certificate setup. & Add Let's Encrypt automation using Certbot or \texttt{nginx-proxy} companion container with automatic SSL renewal. \\
    \hline
    L-18 & \textbf{Manual deployment step} & Operations & After new image is built and pushed, admin must manually run \texttt{docker-compose pull \&\& up -d} on production server. & Implement automated deployment webhook that triggers on image push to update production automatically. \\
    \hline
    \caption{Operational Limitations and Proposed Mitigations}
    \label{tab:ops-limitations}
\end{longtable}
\endgroup

\section{Future Work Roadmap}
\label{sec:future-work}

\subsection{Short-Term Improvements (1-2 Sprints)}

\begin{table}[htbp]
    \centering
    \renewcommand{\arraystretch}{1.3}
    \small
    \begin{tabular}{|c|p{4.2cm}|c|p{3.8cm}|}
        \hline
        \textbf{Priority} & \textbf{Feature} & \textbf{Effort} & \textbf{Impact} \\
        \hline
        \textcolor{red}{\ding{108}} High & \textbf{Automated database backups} (L-15) & 1 day & Critical data protection \\
        \hline
        \textcolor{red}{\ding{108}} High & \textbf{HTTPS with Let's Encrypt} (L-17) & 1 day & Security requirement for production \\
        \hline
        \textcolor{orange}{\ding{108}} Medium & \textbf{Email notifications for grades} (L-09) & 3-5 days & Improved student experience \\
        \hline
        \textcolor{orange}{\ding{108}} Medium & \textbf{GPA calculation} (L-14) & 2-3 days & Academic reporting requirement \\
        \hline
        \textcolor{yellow}{\ding{108}} Low & \textbf{Multi-attempt quizzes} (L-13) & 1-2 days & Enhanced assessment flexibility \\
        \hline
    \end{tabular}
    \caption{Short-Term Improvement Roadmap (1-2 Sprints)}
    \label{tab:short-term}
\end{table}

\subsection{Medium-Term Improvements (3-6 Sprints)}

\begin{table}[htbp]
    \centering
    \renewcommand{\arraystretch}{1.3}
    \small
    \begin{tabular}{|c|p{4.2cm}|c|p{3.8cm}|}
        \hline
        \textbf{Priority} & \textbf{Feature} & \textbf{Effort} & \textbf{Impact} \\
        \hline
        \textcolor{red}{\ding{108}} High & \textbf{Analytics dashboard} (L-10) & 2-3 sprints & Data-driven academic decisions \\
        \hline
        \textcolor{orange}{\ding{108}} Medium & \textbf{WebSocket real-time updates} (L-03) & 2-3 sprints & Live grade/attendance notifications \\
        \hline
        \textcolor{orange}{\ding{108}} Medium & \textbf{Monitoring with Prometheus/Grafana} (L-16) & 1-2 sprints & Operational visibility \\
        \hline
        \textcolor{orange}{\ding{108}} Medium & \textbf{Celery task queue} (L-04) & 1-2 sprints & Non-blocking bulk operations \\
        \hline
    \end{tabular}
    \caption{Medium-Term Improvement Roadmap (3-6 Sprints)}
    \label{tab:medium-term}
\end{table}

\newpage
\subsection{Long-Term Vision (6+ Sprints)}

\begin{table}[htbp]
    \centering
    \renewcommand{\arraystretch}{1.3}
    \small
    \begin{tabular}{|c|p{4.5cm}|c|p{3.5cm}|}
        \hline
        \textbf{Priority} & \textbf{Feature} & \textbf{Effort} & \textbf{Impact} \\
        \hline
        \textcolor{orange}{\ding{108}} Medium & \textbf{Mobile application} (React Native) (L-07) & 4-6 sprints & Native mobile experience \\
        \hline
        \textcolor{orange}{\ding{108}} Medium & \textbf{Messaging system} (L-08) & 3-4 sprints & Two-way communication \\
        \hline
        \textcolor{yellow}{\ding{108}} Low & \textbf{Multi-language support} (L-12) & 2-3 sprints & International accessibility \\
        \hline
        \textcolor{yellow}{\ding{108}} Low & \textbf{Horizontal scaling} (K8s) (L-01) & 3-4 sprints & Enterprise-grade scalability \\
        \hline
        \textcolor{yellow}{\ding{108}} Low & \textbf{Automated proctoring} (L-11) & 4-6 sprints & Academic integrity enhancement \\
        \hline
        \textcolor{orange}{\ding{108}} Medium & \textbf{Discussion Forums} (L-19) & 2-3 sprints & Asynchronous academic engagement \\
        \hline
        \textcolor{orange}{\ding{108}} Medium & \textbf{Live Virtual Classrooms} (L-20) & 4-5 sprints & Real-time remote learning \\
        \hline
    \end{tabular}
    \caption{Long-Term Vision Roadmap (6+ Sprints)}
    \label{tab:long-term}
\end{table}

\newpage
\subsection{Architecture Evolution Path}

\begin{figure}[htbp]
    \centering
    \begin{minipage}{0.45\textwidth}
        \centering
        \textbf{Current State (stable)}\\[0.5em]
        \begin{tabular}{|l|}
            \hline
            Django Monolith \\
            2 Gunicorn Workers \\
            MySQL (single) \\
            Redis (Sessions + Cache) \\
            HTTP \\
            Manual Deploy \\
            No Monitoring \\
            \hline
        \end{tabular}
    \end{minipage}
    \hfill
    $\rightarrow$
    \hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \textbf{Future State}\\[0.5em]
        \begin{tabular}{|l|}
            \hline
            Django + Celery \\
            Async Workers \\
            MySQL + Read Replica \\
            Redis (Sessions + Cache + Broker) \\
            HTTPS (Let's Encrypt) \\
            Auto-Deploy Webhook \\
            Prometheus + Grafana \\
            \hline
        \end{tabular}
    \end{minipage}
    \caption{Architecture Evolution---Current State to Future State}
    \label{fig:architecture-evolution}
\end{figure}

